\documentclass[11pt,oneside]{article}
\usepackage[margin=1.9cm,bindingoffset=0cm]{geometry}
\usepackage{fontspec}
\setmainfont{Frutiger LT Pro}[
  UprightFont = {*Light},
  BoldFont = {*Bold},
  ItalicFont = {*Light Italic},
  BoldItalicFont = {*Bold Italic}]
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue}
\renewcommand{\UrlFont}{\fontspec{Frutiger LT Pro}[
  UprightFont = {*Light},
  ItalicFont = {*Light Italic}]}
\usepackage{enumitem}
\usepackage{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{.5pt}
\titlespacing*{\section}{0pt}{9pt}{3pt}
\titlespacing*{\subsection}{0pt}{9pt}{3pt}
\setlist[itemize]{topsep=3pt, partopsep=0pt, itemsep=3pt, parsep=1.5pt, after=\vspace{0pt}}  
\setlist[enumerate]{topsep=3pt, partopsep=0pt, itemsep=3pt, parsep=1.5pt, after=\vspace{0pt}}
\renewcommand{\baselinestretch}{.9}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancypagestyle{firstpage}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \fancyfoot[L]{May 14, 2025}
  \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}}
\fancypagestyle{main}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0.75pt}
  \fancyhead[L]{Alexander Abuabara}
  \fancyfoot[L]{May 14, 2025}
  \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}}

\begin{document}
\pagestyle{firstpage}
\raggedright

\section*{Alexander Abuabara}
Mail: INDUSTRIAL \& SYSTEMS ENGINEERING MS 3131\\
\hspace{0.9cm} TAMU College Station, TX 77843\\[1pt]
Website: \url{https://abuabara.github.io}\\[1pt]
Email: \href{abuabara@tamu.edu}{abuabara@tamu.edu}\\[1pt]
Phone: +1 979.845.7813

\subsection*{Education}
\begin{itemize}[leftmargin=20pt]
\item Ph.D. in Urban and Regional Science, Texas A\&M University, College Station (2022)\\[1pt]
      Dissertation: Applications of Causal Bayesian Networks in Urban Planning\\[1pt]
      Committee Members: Walter G. Peacock (chair), Zenon Medina-Cetina (chair), Douglas Wunneburger, David Bierling
\item Master of Science in Production Engineering, Federal University of São Carlos, Brazil (2006)\\[1pt]
      Thesis: A Mixed Integer Programming Approach Applied to Multi-Period Industrial Planning\\[1pt]
      Committee Members: Reinaldo Morabito (chair), Horacio Hideki Yanasse, Marcos Nereu Arenales, Denise Sato Yamashita\\[0pt]
      {\small (original in Portuguese)}
\item Bachelor of Science in Civil Engineering, University of São Paulo, Brazil (2001)
\end{itemize}

\subsection*{Academic Positions}
{Wm Michael Barnes ’64 Department of Industrial and Systems Engineering, Texas A\&M University}
\begin{itemize}[leftmargin=20pt]
\item Instructional Assistant Professor (Fall 2025--present)\\
      Supervisor: Lewis Ntaimo
\end{itemize}

\vspace{3pt}

{Department of Landscape Architecture and Urban Planning, Texas A\&M University}\\
\begin{itemize}[leftmargin=20pt]
\item Instructional Assistant Professor (2024--2025)\\
      Supervisor: Galen D. Newman
\item Postdoctoral Research Associate (2022--2024)\\
      Supervisors: Walter G. Peacock, Galen D. Newman
\end{itemize}

\subsection*{Teaching}

\textbf{Fall 2025 Onwards}\\

\vspace{3pt}

{Wm Michael Barnes ’64 Department of Industrial and Systems Engineering, Texas A\&M University}\\
\vspace{3pt}
\begin{itemize}[leftmargin=20pt]
\item DAEN 300 Data Engineering Coding Experience I (Fall 2025)
\item DAEN 301 Data Engineering Coding Experience II (Spring 2026)
\item DAEN 427/ISEN 627 Decision and Risk Analysis (graduate-level; Fall 2025, Spring 2026)
\item DAEN 459 Capstone Senior Design Planning (Fall 2025)
\item DAEN 460 Capstone Senior Design (Spring 2026)
\end{itemize}

\textbf{Courses Taught} (\emph{average teaching evaluation 4.54})\\

\vspace{3pt}

{Department of Landscape Architecture and Urban Planning, Texas A\&M University}
\begin{itemize}[leftmargin=20pt]
\item URPN 201 Evolving Cities (Fall 2021, Spring 2024)
\item URPN 210 Urban Analytical Methods I (Fall and Spring 2019, 2020, 2021, 2022, 2023, 2024)
\item URPN 310 Urban Analytical Methods II (Fall 2024)
\item URPN 325 Introduction to GIS in Urban and Regional Planning (Fall 2024, Spring 2025)
\item URPN 326/PLAN 626 Advanced GIS in Urban and Regional Planning (graduate-level; Spring 2025)
\item PLAN 604 Planning Methods I (graduate-level; Fall 2023, 2024)
\item URSC 642 Analytical Methods II (graduate-level; Spring 2024)
\item FYEX 101 First Year Experience (Fall 2022)
\end{itemize}

\newpage
\pagestyle{main}

\textbf{Guest Lecturer}

\vspace{3pt}

{Department of Landscape Architecture and Urban Planning, Texas A\&M University}
\begin{itemize}[leftmargin=20pt]
\item URPN 361 Urban Issues, presenting \emph{GIS in Planning Communities} (Fall 2022)\\
      Instructor: Madhavi Dixit
\item PLAN 610 Structure and Function of Urban Settlements, presenting \emph{Urban Sprawl} (Fall 2016)\\
      Instructor: Han Park
\item URSC 631 Foundations of Planning, presenting \emph{Natural Hazards Research} (Spring 2025)\\
      Instructors: Sinan Zhong, Ji Won Nam
\end{itemize}

\vspace{3pt}

\textbf{Teaching Assistant}

\vspace{3pt}

{Department of Landscape Architecture and Urban Planning, Texas A\&M University}
\begin{itemize}[leftmargin=20pt]
\item URPN 201 Evolving Cities (Spring 2017)\\
      Instructor: Yu Xiao
\item URSC 642 Analytic Methods II (Spring 2017, 2018, 2019)\\
      Instructor: Walter G. Peacock
\end{itemize}

\vspace{3pt}

{Department of Production Engineering, Federal University of Sao Carlos, Brazil}
\begin{itemize}[leftmargin=20pt]
\item Coding, Introduction to Production Engineering (Spring 2006)\\
      Instructor: Reinaldo Morabito
\item Operations Research Applied to Management (Fall 2005)\\
      Instructor: Reinaldo Morabito
\item Operations Research Applied to Logistics (Fall 2005)\\
      Instructor: Reinaldo Morabito
\end{itemize}

\subsection*{Research}

{Peer Reviewed Journals}\\{\small (Google Scholar: \url{https://scholar.google.com/citations?hl=en&user=r7vp11AAAAAJ})}
\begin{enumerate}[leftmargin=20pt]
\item Blanks, J., Abuabara, A., Roberts, A., Semien, J. (2021). Preservation at the Intersections: Patterns of Disproportionate Multihazard Risk and Vulnerability in Louisiana's Historic African American Cemeteries. \emph{Environmental Justice, 14} (1), 1-14.
\item Horney, J., Karaye, I., Abuabara, A., Gearhart, S., Grabich, S., Perez-Patron, M. (2020). The Impact of Natural Disasters on Suicide in the United States. \emph{Crisis, 42} (5), 328-334.
\item Abuabara, A., Abuabara, A., Tonchuk, C. (2017). Comparative Analysis of Death by Suicide in Brazil and in the United States: descriptive, cross-sectional time series study. \emph{Sao Paulo Medical Journal, 135}, 150-156.
\item Abuabara, A., Morabito, R. (2009). Cutting Optimization of Structural Tubes to Build Agricultural Light Aircrafts. \emph{Annals of Operations Research, 169} (1), 149-165.
\item Abuabara, A., Morabito, R. (2008). Modelos de Programação Inteira Mista para o Planejamento do Corte Unidimensional de Tubos Metálicos na Indústria Aeronáutica Agrícola. \emph{Gestão \& Produção, 15} (3), 605-617.
\end{enumerate}

\vspace{3pt}

{Reports}
\begin{enumerate}[leftmargin=20pt]
\item Lee, R. J., Day, W., Abuabara, A., Newman, G., Peacock, W. G. (2023). The Effect of Flood Buyouts on Nearby Property Values. Working paper for the \emph{Lincoln Institute of Land Policy}.
\item Rosenheim, N., Lane, G., Katare, A., Watson, M., Williams, A., Peacock, W. G., Abuabara, A., Perez, M., Sullivan, E., Kastor, H. (2021). Food Retailer Data, in \emph{Food Access Impact Survey for Harris County and Southeast Texas after Hurricane Harvey in 2017}.
\item Peacock, W. G., Abuabara, A., Wunneburger, D., Bierling, D., Mullins, J. A., Borchardt, D. (2020). Coastal Bend Hurricane Evacuation Study: Evacuation Zone Development Report.
\item Peacock, W. G., Wunneburger, D., Abuabara, A., Bierling, D., Mullins, J. A., Borchardt, D. (2020). Coastal Bend Hurricane Evacuation Study: Vulnerability Analysis Report.
\item Bierling, D., Lindell, M., Peacock, W. G., Abuabara, A., Moore, R., Wunneburger, D., Mullins, J. A., Borchardt, D. (2020). Coastal Bend Hurricane Evacuation Study: Hurricane Harvey Evacuation Behavior Survey Outcomes and Findings.
\item Mullins, J. A., Borchardt, D., Bierling, D., Peacock, W. G., Wunneburger, D., Abuabara, A. (2020). Coastal Bend Hurricane Evacuation Study: Transportation Analysis Report.
\item Peacock, W. G., Wunneburger, D., Abuabara, A., Park, H., Van Zandt, S. (2016). Rio Grande Valley Hurricane Evacuation Study: Vulnerability Analysis Report.
\end{enumerate}

\vspace{3pt}

{Data}
\begin{itemize}[leftmargin=20pt]
\item Lane, G., Rosenheim, N., Williams, A., Watson, M., Abuabara, A., Maher, D., Rathburn, A., Peacock, W. G. (2024). Food Aid Agency Data, in Food Access Impact Survey for Harris County and Southeast Texas after Hurricane Harvey in 2017. DesignSafe-CI.
\end{itemize}

\vspace{3pt}

{Conferences with Peer Reviewed Abstracts}\\{\small (underlined name indicates the presenter)}
\begin{enumerate}[leftmargin=20pt]
\item \underline{Day, W.}, Abuabara, A., Peacock, W. G., Wade, H. FEMA's Financial Housing Assistance to Owners and Renters After Hurricane Harvey. \emph{49th Natural Hazards Workshop}. Broomfield (Jul 2024)
\item \underline{Blanks, J.}, Abuabara, A. Did You Check on the Cemetery? A Geospatial Risk Assessment of Cemeteries in Southeast Louisiana. \emph{PRIMR Conference at PVAMU}. Prairie View (Mar 2023)
\item \underline{Abuabara, A.}, Day, W., Peacock, W. G., Wade, H. An Analysis of FEMA's Individual Assistance After Hurricane Harvey. \emph{Natural Hazards Research Summit}. Washington DC (Oct 2022)
\item \underline{Abuabara, A.}, Peacock, W. G., Bierling, D., Lindell, M. A Statistical Analysis of Household Evacuation in Response to Hurricane Harvey. \emph{Society for Risk Analysis Annual Meeting}. Austin (Dec 2020)
\item \underline{Abuabara, A.}, Medina-Cetina, Z., Peacock, W. G. Application of Bayesian Networks to Hurricane Risk Assessment. \emph{Society for Risk Analysis Annual Meeting}. Arlington (Dec 2019)
\item \underline{Horney, J.}, Karaye, I., Gearhart, S., Abuabara, A., Perez-Patron, M. Impact of Natural Disasters on Suicide Risk in the United States. \emph{American Public Health Association Annual Meeting}. Philadelphia (Nov 2019)
\item \underline{Abuabara, A.}, Peacock, W. G. Importance of Mobile Homes to Determine Natural Hazard Evacuation Boundaries. \emph{46th Natural Hazards Workshop}. Broomfield (Jul 2017)
\item \underline{Abuabara, A.}, Considerations for Modeling Natural Hazard Evacuation of Mobile Neighborhoods and Mobile Parks in the Texas Valley Region. \emph{42nd Urban Affairs Assoc. Conference}. San Diego (Mar 2016)
\item Abuabara, A.,\underline{ Morabito, R.} Modelo de Otimização de Corte Unidimensional Aplicado a Fabricação de Aeronaves Agrícolas, \emph{Annals of XXXIX Simpósio Brasileiro de Pesquisa Operacional}. Fortaleza, Brazil (Aug 2007)
\item \underline{Morabito, R.}, Abuabara, A. A One-dimensional Cutting Stock Problem in the Production of Agricultural Light Aircrafts”, \emph{XXII European Conference on Operational Research}, Prague, Czech Republic (Jul 2007)
\item \underline{Abuabara, A.}, Morabito, R. Pipe Cutting Optimization: Application to the Aeronautics Industry. \emph{Latin-Iberoamerican Conference on Operations Research} CLAIO. Montevideo, Uruguay (Nov 2006)
\end{enumerate}

\vspace{3pt}

{Workshops, Conferences, and Seminars}
\begin{enumerate}[leftmargin=20pt]
\item Problem Structuring, Data, and My Teaching Journey, and Why My Students Still Ask for Extra Credit. ISEN Spring Seminar (2025)
\item Hurricane Evacuation Studies: Zone Planning for Coastal Texas. CoA Research Symposium (2024)
\item Application of Bayesian Networks to Hurricane Risk Assessment. CoA Research Symposium (2024)
\item Modeling Individual Assistance to Households ​in Texas After Hurricane Harvey. CoA Research Symposium (2024)
\item Hurricane Evacuation Studies: Zone Planning for Coastal Texas. CoA Research Symposium (2024)
\item Modeling Individual Assistance to Households ​in Texas After Hurricane Harvey. CoA Research Symposium (2023)
\item A Web-Based GIS Platform and Applications for Evacuation, Preparedness, Response, Mitigation, and Recovery Planning: The Texas Hazard Resilience Atlases. Texas Emergency Management Conference (2023)\\
\item FEMA Individual Assistance Program for Housing. IN-CORE Summer Research Meeting (2022)
\item Hurricane Evacuation Studies. Texas A\&M University/GEOSAT Seminar (2018)
\item Texas GIS Day (2018, 2019, 2020, 2021)\\
      Supervisor: Daniel Goldberg
\begin{itemize}
\item Introduction to QGIS
\item Spatial Analysis in R
\end{itemize}
\end{enumerate}

%\newpage

\subsection*{Research Experience}
{Department of Landscape Architecture and Urban Planning, Texas A\&M University}
\begin{itemize}[leftmargin=20pt]
\item \emph{Graduate Research Lecturer} (2019-2022)\\
      Advisors: Walter G. Peacock and Galen Newman
\item \emph{Graduate Research Assistant} (2015-2022)\\
      Advisor: Walter G. Peacock
\end{itemize}

\vspace{3pt}

{Research Projects Collaboration}
\begin{enumerate}[leftmargin=20pt]
\item Safeguarding Texas's Inland Rural Heritage: Collaborative Strategies for Resilience Against Natural Hazards (upcoming Spring 2026). \emph{Center for Heritage Conservation, Texas A\&A University.}
\item Hurricane Evacuation Studies: (i) Southeastern Texas (2024-2025), (ii) Texas Coastal Bend (2018-2019), and (iii) Texas Valley (2014-2016). \emph{US Army Corps of Engineers}.
\item Risk-Based Community Resilience Planning (2022-2024). \emph{National Institute of Standards and Technology}.
\item The Adoption and Utilization of Hazard Mitigation Practices by Jurisdictions along Gulf and Atlantic Coasts (2016-2018). \emph{National Science Foundation}.
\end{enumerate}

\subsection*{Service}
\begin{itemize}[leftmargin=20pt]
\item Faculty Senator, College of Architecture (2024-2025)\\
      COA Faculty Senator Caucus Leader: Shelley D. Holliday, Senate Speaker: Angie Hill Price
\end{itemize}

\subsection*{Honors, Fellowships, Awards}

{Professional Development}
\begin{itemize}[leftmargin=20pt]
\item Faculty Affairs Third-Party Conflict Resolution Mediator, Texas A\&M University (Fall 2024)\\
      Associate Provost for Faculty Affairs: Heather Wilkinson
\item Graduate Graduate Mentoring Academy Fellow, Texas A\&M University (Fall 2024)\\
      Assistant Director of Mentoring \& Graduate Education: Clinton A. Patterson
\end{itemize}

\vspace{3pt}

{Professional Affiliations and Memberships}
\begin{itemize}[leftmargin=20pt]
\item Center for Geospatial Sciences, Applications and Technology Fellow, Texas A\&M University (2020-present)
\item Stochastic Geomechanics Laboratory Fellow, Texas A\&M University (2018-present)
\item Hazard Reduction and Recovery Center Fellow, Texas A\&M University (2015-present)
\item Society for Risk Analysis (2018-present)
\item Tau Sigma Delta Honor Society (2015-present)
\item Regional Council of Engineering and Agronomy of São Paulo, Brazil (2002-2005)
\end{itemize}

\newpage
%\vspace{3pt}

{Honors and Fellowships}
\begin{itemize}[leftmargin=20pt]
\item {Full Tuition Assistantship}, Texas A\&M University (2015-2022)
\item {Travel Award for Natural Hazards Research Summit}, National Science Foundation, Washington DC (Oct 2022)
\item {Summer Institute for Early-Career Faculty Award}, National Science Foundation Natural Hazards Engineering Research Infrastructure (NHERI), San Antonio, TX (Jun 2022)
\item {Open-Source GIS Developers Summer School}, GeoSTAT Institute of Botany of the Czech Academy of Sciences (IBOT), Prague, Czech (Aug 2018)
\item {Coastal Flood Risk Reduction Research}, National Science Foundation Partnerships for International Research and Education (PIRE), Amsterdam, Netherlands (May 2018)
\item {Graduate Program Scholarship}, Department of Landscape Architecture and Urban Planning, Texas A\&M University (2014-2015)
\item {Graduate Program Scholarship}, Department of Production Engineering, Federal University of Sao Carlos, Brazil (2005-2006)
\end{itemize}

\subsection*{Non-academic Positions}
\begin{itemize}[leftmargin=20pt]
\item Civil Engineer, Sucocitrico Cutrale Ltd., Araraquara, Brazil (2002-2005)\\
      Supervisor: Marcos Neves Penteado Moraes
\item Civil Engineer Trainee, University of São Paulo, São Carlos, Brazil (1999-2000)\\
      Supervisor: Manoel Rodrigues Alves
\end{itemize}

\end{document}