\documentclass[11pt]{article}
\usepackage[left=2.1cm, right=2.1cm, bottom=1.9cm, top=1.9cm]{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{.5pt}
\titlespacing*{\section}{0pt}{9pt}{3pt}
\titlespacing*{\subsection}{0pt}{9pt}{6pt}
\setlist[itemize]{topsep=3pt, partopsep=0pt, itemsep=3pt, parsep=1.5pt, after=\vspace{0pt}}  
\setlist[enumerate]{topsep=3pt, partopsep=0pt, itemsep=3pt, parsep=1.5pt, after=\vspace{0pt}}
\renewcommand{\baselinestretch}{.93}
\pagestyle{fancyplain}
\lfoot{May 14, 2025} \cfoot{}
\begin{document}
\raggedright

\section*{Alexander Abuabara, Ph.D.}
Website: \url{https://abuabara.github.io}\\[1pt]
Email: \href{mailto:abuabara@tamu.edu}{abuabara@tamu.edu}

\subsection*{Education}
\begin{itemize}[leftmargin=20pt]
\item Ph.D. in Urban and Regional Science , Texas A\&M University, College Station (2022)\\[1pt]
      Dissertation: Applications of Causal Bayesian Networks in Urban Planning
\item Master of Science in Production Engineering, Federal University of São Carlos, Brazil (2006)\\[1pt]
      Thesis: A Mixed Integer Programming Approach Applied to Multi-Period Industrial Planning\\
      {\small (original in Portuguese)}
\item Bachelor of Science in Civil Engineering, University of São Paulo, Brazil (2001)
\end{itemize}

\subsection*{Academic positions}
Wm Michael Barnes ’64 Department of Industrial and Systems Engineering, Texas A\&M University
\begin{itemize}[leftmargin=20pt]
\item Instructional Assistant Professor (2025-present)
\end{itemize}

\vspace{3pt}

Department of Landscape Architecture and Urban Planning, Texas A\&M University
\begin{itemize}[leftmargin=20pt]
\item Instructional Assistant Professor (2024-2025)
\item Postdoctoral Research Associate (2022-2024)
\end{itemize}

\subsection*{Teaching}
\begin{itemize}[leftmargin=20pt]
\item DAEN 427/ISEN 427 Decision and Risk Analysis
\item DAEN 459 Capstone Senior Design Planning
\item DAEN 460 Capstone Senior Design
\item DAEN 300 Data Engineering Coding Experience I
\item DAEN 301 Data Engineering Coding Experience II
\end{itemize}

\subsection*{Service}
\begin{itemize}[leftmargin=20pt]
\item Faculty Senator, College of Architecture (2024-2025)
\end{itemize}

\subsection*{Papers}
\url{https://scholar.google.com/citations?hl=en&user=r7vp11AAAAAJ}
\begin{enumerate}[leftmargin=20pt]
\item Abuabara, A., \& Morabito, R. (2009). Cutting optimization of structural tubes to build agricultural light aircrafts. \emph{Annals of Operations Research, 169} (1), 149-165.
\item Horney, J. Karaye, I., Abuabara, A., Gearhart, S., Grabich, S. \& Perez-Patron, M. (2020). The Impact of Natural Disasters on Suicide in the United States. \emph{Crisis, 42} (5), 328-334.
\item Blanks, J., Abuabara, A., Roberts, A., \& Semien, J. (2021). Preservation at the Intersections: Patterns of Disproportionate Multihazard Risk and Vulnerability in Louisiana's Historic African American Cemeteries. \emph{Environmental Justice, 14} (1), 1-14.
\end{enumerate}

\subsection*{Research projects collaboration}
\begin{itemize}[leftmargin=20pt]
\item Hurricane Evacuation Studies: (i) Southeastern Texas (2024-2025), (ii) Texas Coastal Bend (2018-2019), and (iii) Texas Valley (2014-2016). \emph{US Army Corps of Engineers}.
\item Risk-Based Community Resilience Planning (2022-2024). \emph{National Institute of Standards and Technology}.
\item The Adoption and Utilization of Hazard Mitigation Practices by Jurisdictions along Gulf and Atlantic Coasts (2016-2018). \emph{National Science Foundation}.
\end{itemize}

\end{document}