\documentclass[article,8pt]{article}
\renewcommand{\baselinestretch}{.85}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
%\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[left=1in,right=1in,bottom=1in,top=1in]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\lfoot{Last updated \today} \cfoot{} \rfoot{\thepage}
\date{\today}
\title{}
\begin{document}

\section*{Alexander Abuabara, Ph.D.}

Department of Landscape Architecture and Urban Planning\\[1pt]
Texas A\&M University\\[1pt]
Email: abuabara@tamu.edu\\[1pt]
Website: \url{https://abuabara.github.io}

\subsection*{Education}
\begin{itemize}
\item Ph.D., Urban and Regional Science, Texas A\&M University, College Station, 2022
\item M.S., Production Enginnering, Federal University of São Carlos, Brazil, 2006
\item B.S., Civil Enginnering, University of São Paulo, Brazil, 2001
\end{itemize}

\subsection*{Academic positions}
Department of Landscape Architecture \& Urban Planning, Texas A\&M University
\begin{itemize}
\item 2024-present: Instructional Assistant Professor
\item 2022-2024: Postdoctoral Research Associate
\item 2021-2022: Graduate Assistant Lecturer
\item 2015-2022: Graduate Research Assistant
\end{itemize}

\subsection*{Teaching}
%Department of Landscape Architecture \& Urban Planning, Texas A\&M University
\begin{itemize}
\item URPN 210, URPN 310: Analytical Methods I \& II
\item PLAN 604: Planning Methods (graduate-level)
\item URSC 642: Analytical Methods II (graduate-level)
\item URPN 325, URPN 326: Introductory \& Advanced GIS
\item PLAN 625, PLAN 626: Introductory \& Advanced GIS (graduate-level)
\end{itemize}

\subsection*{Papers}
\url{https://scholar.google.com/citations?hl=en&user=r7vp11AAAAAJ}
\begin{enumerate}
\item Blanks, J., Abuabara, A., Roberts, A., \& Semien, J. (2021). Preservation at the Intersections: Patterns of Disproportionate Multihazard Risk and Vulnerability in Louisiana's Historic African American Cemeteries. \emph{Environmental Justice, 14} (1), 1-14.
\item Horney, J. Karaye, I., Abuabara, A., Gearhart, S., Grabich, S. \& Perez-Patron, M. (2020). The Impact of Natural Disasters on Suicide in the United States. \emph{Crisis, 42} (5), 328-334.
\item Abuabara, A., \& Morabito, R. (2009). Cutting optimization of structural tubes to build agricultural light aircrafts. \emph{Annals of Operations Research, 169} (1), 149-165.
\end{enumerate}

\subsection*{Research}
\begin{itemize}
\item Risk-Based Community Resilience Planning (2022-2024). National Institute of Standards and Technology.
\item Hurricane Evacuation Studies: Southeastern Texas (2024-1025), Texas Coastal Bend (2018-1019), and Texas Valley (2014-1016). US Army Corps of Engineers.
\item The Adoption and Utilization of Hazard Mitigation Practices by Jurisdictions along Gulf and Atlantic Coasts (2016-2018). National Science Foundation.
\end{itemize}

\subsection*{Service}
\begin{itemize}
\item 2024-present: Interim Faculty Senator, College of Architecture
\end{itemize}

%\subsection*{Mentoring}
%Masters Thesis Chair
%\begin{enumerate}
%\item JenWei Huang (in progress)
%\end{enumerate}

\end{document}